---
title: "Creating Custom Palettes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Creating Custom Palettes}
  %\VignetteEngine{rmarkdown::render}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Creating Custom Palettes

This guide explains how to add your own custom color palettes to vibeColors.

## Adding Palettes to the Package

To add a new palette, you need to edit the `vibe_palettes` list in the `R/pal.

## Palette Structureettes.R` file

Each palette should be a named character vector of hex color codes:

```r
vibe_palettes <- list(
  my_palette = c("#FF6B6B", "#4ECDC4", "#45B7D1", "#96CEB4", "#FFEAA7")
)
```

## Guidelines for Good Palettes

### 1. Use Meaningful Colors

Choose colors that are:
- **Distinct**: Colors should be easily distinguishable from each other
- **Accessible**: Consider colorblind-friendly palettes
- **Cohesive**: Colors should work well together as a group

### 2. Consider Color Theory

- **Complementary**: Colors opposite on the color wheel
- **Analogous**: Colors adjacent on the color wheel
- **Triadic**: Three colors equally spaced on the color wheel
- **Sequential**: Colors that progress from light to dark (or vice versa)

### 3. Test Your Palettes

Use the built-in functions to test your palettes:

```{r test-palette}
library(vibeColors)
library(ggplot2)

# After adding your palette to vibe_palettes list:
# palette_preview("my_palette")
```

## Example: Creating a Sequential Palette

Sequential palettes are great for showing ordered data:

```r
vibe_palettes <- list(
  ocean = c("#F7FBFF", "#DEEBF7", "#C6DBEF", "#9ECAE1",
            "#6BAED6", "#4292C6", "#2171B5", "#08519C", "#08306B")
)
```

## Example: Creating a Categorical Palette

Categorical palettes work best for discrete data:

```r
vibe_palettes <- list(
  sunset = c("#FF6B6B", "#FFA07A", "#FFD700", "#FF8C00", "#FF4500")
)
```

## Testing Your Palette with ggplot2

```{r test-ggplot, eval=FALSE}
# Test with a simple plot
ggplot(iris, aes(Species, Sepal.Length, fill = Species)) +
  geom_bar(stat = "identity") +
  scale_fill_vibe("my_palette")
```

## Exporting Your Palette

The `vibe_palette()` function allows you to retrieve and customize your palette:

```{r export-example, eval=FALSE}
# Get raw colors
vibe_palette("my_palette")

# Get more colors through interpolation
vibe_palette("my_palette", n = 10)

# Reverse the palette
vibe_palette("my_palette", reverse = TRUE)
```

## Best Practices

1. **Start with 3-5 colors** for categorical palettes
2. **Use 9 colors** for sequential palettes (standard for ggplot2)
3. **Test with real data** before finalizing
4. **Consider accessibility** for colorblind users

## Next Steps

- Check the [Getting Started](vibeColors.html) guide for basic usage
- Explore the reference documentation for all available functions
