---
title: "Getting Started with vibeColors"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with vibeColors}
  %\VignetteEngine{rmarkdown::render}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

vibeColors is an R package that provides a collection of color palettes designed for use with ggplot2. This vignette will walk you through the basics of using vibeColors in your data visualization projects.

## Installation

You can install the development version of vibeColors from GitHub:

```r
# install.packages("devtools")
devtools::install_github("yourusername/vibeColors")
```

## Listing Available Palettes

To see all available palettes in the package:

```{r setup}
library(vibeColors)

# List all available palettes
list_vibe_palettes()
```

## Using Palettes with ggplot2

vibeColors provides several scale functions that integrate seamlessly with ggplot2:

### Discrete Scales

For categorical data, use the discrete scale functions:

```{r discrete-example, eval=FALSE}
library(ggplot2)

# Example with discrete data
ggplot(mtcars, aes(factor(cyl), fill = factor(cyl))) +
  geom_bar() +
  scale_fill_vibe("palette_name")
```

### Continuous Scales

For continuous data, use the continuous scale functions:

```{r continuous-example, eval=FALSE}
# Example with continuous data
ggplot(mtcars, aes(wt, mpg, color = hp)) +
  geom_point(size = 3) +
  scale_color_vibe_c("palette_name")
```

## Palette Reversal

You can reverse any palette by setting `reverse = TRUE`:

```{r reverse-example, eval=FALSE}
ggplot(mtcars, aes(factor(cyl), fill = factor(cyl))) +
  geom_bar() +
  scale_fill_vibe("palette_name", reverse = TRUE)
```

## Custom Number of Colors

When using discrete scales, you can request more colors than are in the original palette. The package will automatically interpolate to create additional colors:

```{r n-colors-example, eval=FALSE}
# Get 10 colors from a palette that has fewer
vibe_palette("palette_name", n = 10)
```

## Next Steps

- Check out the [Creating Palettes](creating-palettes.html) article to learn how to add your own custom palettes
- Explore the reference documentation for detailed information on each function
